The hydra and the rooster

### 2020-07-08 latex/chapter-skippable.tex
redaction chapter on ordinal notations

\paragraph{Related work}
Finite ordinals are also formailzed in MathComp~\cite{SSR}.  See also Adam Chlipala's \emph{CPDT}~\cite{chlipalacpdt2011} for a thorough study of the use of dependent types.

@@

\begin{itemize}
\item $\omega$: \coq's type \texttt{nat}, with the order \texttt{Nat.lt}.
\item $\omega^n$ (for some  integer  $n\geq 2$) : the type of $n$-uples of natural numbers, with the lexicographic product of $n$ copies of \texttt{Nat.lt}.
\item  $\omega^\omega$: the set of nonincreasing sequences of natural numbers, lexicographically ordered (also the set of finite multisets of natural numbers).
\item $\epsilon_0$: The set of terms in Cantor normal form (see Chap.~\ref{chap/T1}).
\item $\Gamma_0$: The set of terms in Veblen normal form.
\end{itemize}

>>>>

\paragraph{Related work}
Finite ordinals are also formalized in MathComp~\cite{SSR}.  See also Adam Chlipala's \emph{CPDT}~\cite{chlipalacpdt2011} for a thorough study of the use of dependent types.

@@

We can also prove that any finite ordinal $i$ can be considered as a sub-segment of $\omega$.

\begin{Coqsrc}
Global Instance FinOrd_Omega (i:nat) :
  SubSegment (FinOrd i) Omega i 
             (fun alpha =>  proj1_sig alpha).
\end{Coqsrc}

\subsection{The ordinal \texorpdfstring{$\omega+\omega$}{omega + omega}}

The ordinal $\omega+\omega$ (also known as $\omega\times 2$) may be represented as the concatenation 
of two copies of $\omega$ (Figure~\ref{fig:omega-plus-omega}).

\begin{figure}[h]
   \centering
   \begin{tikzpicture}[very thick, scale=0.5]
\begin{scope}[color=blue]
\node(A0) at (2,0)[label=below:$0$]{$\bullet$};
\node(A1) at (3,0)[label=below:$1$]{$\bullet$};
\node(A2) at (4,0)[label=below:$2$]{$\bullet$};
\node (Adots) at (6,0) {$\ldots$};
\node(An) at (8,0)[label=below:$n$]{$\bullet$};
\node(A2) at (10,0)[label=below:$n+1$]{$\bullet$};
\node (Adots1) at (12,0) {$\ldots$};
\end{scope}
\begin{scope}[color=red]
\node(B0) at (14,0)[label=below:$0$,label=above:$\omega$]{$\bullet$};
\node(B1) at (16,0)[label=below:$1$, label=above:$\omega+1$]{$\bullet$};
\node(B2) at (18,0)[label=below:$2$,label=above:$\omega+2$]{$\bullet$};
\node (Bdots) at (20,0) {$\ldots$};
\node (Bn) at (22,0) [label=below:$p$, label=above:$\omega+p$]{$\bullet$};
\node (Bdots2) at (24,0) {$\ldots$};
\end{scope}
\end{tikzpicture}
   \caption{\textcolor{blue}{$\omega+{\color{red}\omega}$}}
   \label{fig:omega-plus-omega}
 \end{figure}

In \coq{}, we use the disjoint union \texttt{(nat+nat)\%type} for representing the elements of $\omega+\omega$.
The blue ordinals of Figure~\ref{fig:omega-plus-omega} will be represented by terms of the form \texttt{(inl $i$)},
the red ones by \texttt{(inr $j$)}.

\vspace{4pt}
\noindent\emph{From Module~\href{../src/html/hydras.Prelude.Omega_plus_omega.html}{Prelude.Omega\_plus\_omega}}

\begin{Coqsrc}
Declare Scope oo_scope.
Delimit Scope oo_scope with oo.
Open Scope oo_scope.

Definition t := (nat + nat)%type.
Arguments inl  {A B} _.
Arguments inr  {A B} _.
\end{Coqsrc}

\begin{itemize}
\item $\omega^n$ (for some  integer  $n\geq 2$) : the type of $n$-uples of natural numbers, with the lexicographic product of $n$ copies of \texttt{Nat.lt}.
\item  $\omega^\omega$: the set of nonincreasing sequences of natural numbers, lexicographically ordered (also the set of finite multisets of natural numbers).
\item $\epsilon_0$: The set of terms in Cantor normal form (see Chap.~\ref{chap/T1}).
\item $\Gamma_0$: The set of terms in Veblen normal form.
\end{itemize}
